Exoplanet population inference and the abundance \\ of Earth analogs from noisy, incomplete catalogs

### 2014-08-21 document/ms.tex
moving derivation of inverse-detection-efficiency to appendix

\paragraph{Inverse-detection-efficiency}
It's now interesting to take a brief aside and discuss the connection between
our model and the commonly used inverse-detection-efficiency procedure
(\citealt{howard,dressing,petigura}).
This procedure involves making a weighted histogram of the catalog entries
where the weight for object $\entry_k$ is $1/\completeness(\entry_k)$.
This makes intuitive sense but the standard formulation does not have a clear
probabilistic justification or interpretation.

@@

>>>>

@@

\appendix

\section*{APPENDIX}

\section{Inverse-detection-efficiency}

It's now interesting to take a brief aside and discuss the connection between
our model and the commonly used inverse-detection-efficiency procedure
(\citealt{howard,dressing,petigura}).
This procedure involves making a weighted histogram of the catalog entries
where the weight for object $\entry_k$ is $1/\completeness(\entry_k)$.
This makes intuitive sense but the standard formulation does not have a clear
probabilistic justification or interpretation.
